How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in the Pacific Pond Turtle (\textit{Emys marmorata})

### 2015-09-08 doc/draft_turtle.tex
added seven graph to document

\subsection{Comparison with clear-cut example}
In contrast with the above results, the analysis of the seven morphologically-distinct species demonstrates near perfect classification of the both the in-sample and out-of-sample datasets (Table \ref{tab:second_res}). These results demonstrate that when there are strong distinctions between the states of the classification schemes, the methods used here can recover them.

@@

>>>>

\subsection{Comparison with clear-cut example}
In contrast with the above results, the analysis of the seven morphologically-distinct species demonstrates near perfect classification of the both the in-sample and out-of-sample datasets (Table \ref{tab:second_res}). Additionally, the distribution of ROC scores from 1000 bootstrap replicates are tightly clustered near ROC = 1 (Fig. \ref{fig:seven_boot}), which is contrast to the results from the \textit{E. marmorata} case (Fig. \ref{fig:gen_hist}). These results demonstrate that when there are strong distinctions between the states of the classification schemes, the methods used here can recover them.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[height = \textheight, width = \textwidth, keepaspectratio = true]{figure/seven_boot}
  \caption{Distribution of 1000 bootstrap replicates of the out-of-sample AUC values from the secondary, multi-species dataset. The AUC values are from the random forest (RF), linear discriminate analysis (LDA), and multinomial logistic regression (MLR). AUC values range between 0.5 (no better than random) and 1 (perfect classification).}
  \label{fig:seven_boot}
\end{figure}
